Detection and Classification of Supernova Gravitational Waves Signals: A Deep Learning Approach

### 2020-07-16 main.tex
correct misspelled words

%
% the new test waveofmr procedure
%
Using the procedure described in Sec.~\ref{sec:spwf}, we generate $1.08\times10^6$
samples for each distance and therefore each class has $3.6\times10^5$
samples. The performance of the \ac{CNN} on the test waveforms is shown in
Fig.~\ref{fig:Extratest}. For waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$
at $60$ kpc and a \ac{FAP} of $0.1\%$, the \ac{CNN} achieves a \ac{TAP} of $66\%$
with H+L+VK. This indicates that with the
\ac{CNN} and a network of H+L+VK, it is possible to detect these waveforms from sources that are at
distances consistent with the Large and Small Magellanic Clouds.
For HLVK and a distance of $40$ kpc, a \ac{TAP} of $54\%$ is achieved, showing the possibility of detecting 
these waveforms out to the satellite galaxies within such a distance.
For waveforms $\text{s}20$ and $\text{SFHx}$ and a \ac{FAP} of $0.1\%$, 
the \acp{TAP} for H+L+VK are $91\%$ and $56\%$ for $3$ and $7$ kpc respectively.
For HLVK, the \acp{TAP} is $79\%$ and $50\%$ at $3$ and $5$ kpc.
The efficiency for the waveforms $\text{s}20$ and $\text{SFHx}$ is noticeably
higher than that for the neutrino-driven mechanism in Fig.~\ref{fig:eff} for
the same distance. This is because as mentioned before, the detection and
classification efficiency in Fig.~\ref{fig:eff} are the results averaged over
the testing samples. It is possible that individual waveforms may be easier for
the \ac{CNN} to detect. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}\label{sec:conclusion}
%
% overall main message
%
We have demonstrated that a \ac{CNN} can be applied for the purpose of
distinguishing \ac{GW} detector time series among pure background noise and
\ac{CCSN} explosion mechanisms. We have trained, valided, and tested 
the \ac{CNN} using $1.26\times10^{6}$ samples of simulated time series for each distance at a
number of distances from $0.2$ kpc to $200$ kpc, where the background noise is Gaussian noise. 
The data samples for each class consisted of approximately $4.2\times10^5$ samples. 
Our results have been shown to be at least consistent with or in some situations may even be 
more promising than the results in the literature.
%
% Primary magneto results
%

>>>>

%
% the new test waveofmr procedure
%
Using the procedure described in Sec.~\ref{sec:spwf}, we generate $1.08\times10^6$
samples for each distance and therefore each class has $3.6\times10^5$
samples. The performance of the \ac{CNN} on the test waveforms is shown in
Fig.~\ref{fig:Extratest}. For waveforms $\text{R3E1AC}$ and $\text{R4E1FC\_L}$
at $60$ kpc and a \ac{FAP} of $0.1\%$, the \ac{CNN} achieves a \ac{TAP} of $66\%$
with H+L+VK. This indicates that with the
\ac{CNN} and a network of H+L+VK, it is possible to detect these waveforms from sources that are at
distances consistent with the Large and Small Magellanic Clouds.
For HLVK and a distance of $40$ kpc, a \ac{TAP} of $54\%$ is achieved, showing the possibility of detecting 
these waveforms out to the satellite galaxies within such a distance.
For waveforms $\text{s}20$ and $\text{SFHx}$ and a \ac{FAP} of $0.1\%$, 
the \acp{TAP} for H+L+VK are $91\%$ and $56\%$ for $3$ and $7$ kpc respectively.
For HLVK, the \acp{TAP} is $79\%$ and $50\%$ at $3$ and $5$ kpc.
The efficiency for the waveforms $\text{s}20$ and $\text{SFHx}$ is noticeably
higher than that for the neutrino-driven mechanism in Fig.~\ref{fig:eff} for
the same distance. This is because as mentioned before, the detection and
classification efficiency in Fig.~\ref{fig:eff} are the results averaged over
the testing samples. It is possible that individual waveforms may be easier for
the \ac{CNN} to detect. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}\label{sec:conclusion}
%
% overall main message
%
We have demonstrated that a \ac{CNN} can be applied for the purpose of
distinguishing \ac{GW} detector time series among pure background noise and
\ac{CCSN} explosion mechanisms. We have trained, validated, and tested 
the \ac{CNN} using $1.26\times10^{6}$ samples of simulated time series for each distance at a
number of distances from $0.2$ kpc to $200$ kpc, where the background noise is Gaussian noise. 
The data samples for each class consisted of approximately $4.2\times10^5$ samples. 
Our results have been shown to be at least consistent with or in some situations may even be 
more promising than the results in the literature.
%
% Primary magneto results
%
